CF Registry Analysis - ROC

### 2024-08-27 Christine Chan/CF Registry/cf_registry_ROC_analysis.qmd
CFF GCT study

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(gt)
library(pROC)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/tim/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

@@

For each ROC curve, we performed 2000 bootstrap replicates. Here the median best threshold (based on Youden index), sensitivity, and specificity are presented along with the bootstrapped 95% confidence intervals. Column names are printed in terms of percentiles, so `threshold.2.5.` indicates the lower limit of the confidence interval, `threshold.50.` indicates the median best threshold, and `threshold.97.5.` indicates the upper limit of the confidence interval.

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
```

>>>>

```{r setup}
#| include: false
library(dplyr)
library(tidyr)
library(ggplot2)
library(gtsummary)
library(gt)
library(pROC)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Christine Chan/CF Registry",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Christine Chan/CF Registry",
  "Linux" = "/home/tim/OneDrive/Vigers/CF/Christine Chan/CF Registry"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/tim/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
set.seed(1017)
```

@@

For each ROC curve, we performed 2000 bootstrap replicates. Here the median best threshold (based on Youden index), sensitivity, and specificity are presented along with the bootstrapped 95% confidence intervals. Column names are printed in terms of percentiles, so `threshold.2.5.` indicates the lower limit of the confidence interval, `threshold.50.` indicates the median best threshold, and `threshold.97.5.` indicates the upper limit of the confidence interval. All non-bootstrapped thresholds are also reported.

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = peds_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = adult_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = white_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = black_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = more_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_ngt_agt)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(ogtt ~ hgba1c, data = other_agt_cfrd)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = roc_df)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = peds_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = adult_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = white_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = black_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = more_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(ci.coords(r, "best"))) %>% fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(agt ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```

@@

```{r}
#| message: false
r <- roc(cfrd ~ hgba1c, data = other_roc)
plot(r, print.auc = T, print.thres = T)
gt(data.frame(coords(r, "best"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(ci.coords(r, "best", best.policy = "random"))) %>%
  fmt_number(n_sigfig = 3)
gt(data.frame(coords(r, "all"))) %>% fmt_number(n_sigfig = 3)
```
